Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-03 longSC.tex
ampt footnote

@@

\begin{figure*}
	\begin{center}
        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)). The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$. Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

@@

The centrality dependence of SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version used in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}. The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

@@

%

@@

\begin{figure*}[h]
	\begin{center}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
        Calculations with three initial conditions from AMPT, MC-KLN, and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT are drawn as dashed lines. }
         \label{fig:Figure_3}
        \end{center}   
 \end{figure*}

The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2). 
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
Similarly to hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations and cannot be described by these models quantitively.
However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parameterizations.
Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Hence the calculations with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and AMPT initial condition is favored by the data.

\begin{figure*}[!]
	\begin{center}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various AMPT models. Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$). The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_4}
        \end{center}   
 \end{figure*}

The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), none of the calculations can describe the data and the calculation with the default AMPT setting follows the trend of the data closest. The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe the sign and magnitude of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot reproduce the data and the strength of the correlation is weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.

>>>>

\begin{figure*}
	\begin{center}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)). The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$. Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

@@

@@

The centrality dependence of SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version used in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}. The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

@@

@@

\begin{figure*}[h]
	\begin{center}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
        Calculations with three initial conditions from AMPT, MC-KLN, and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT are drawn as dashed lines. }
         \label{fig:Figure_3}
        \end{center}   
 \end{figure*}
The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2). 
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
Similarly to hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations and cannot be described by these models quantitively.
However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parameterizations.
Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Hence the calculations with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and AMPT initial condition is favored by the data.

\begin{figure*}[!]
	\begin{center}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various AMPT models. Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$). The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_4}
        \end{center}   
 \end{figure*}
The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), none of the calculations can describe the data and the calculation with the default AMPT setting follows the trend of the data closest. The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe the sign and magnitude of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot reproduce the data and the strength of the correlation is weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.
